Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-08-19 Docs/Paper/LaTex/template.tex
Fixed tex errors

@@

%1
\bibitem{Arató2003}
Arató, P., Juhász, S., Mann, Z.A., Orbán, A., Papp, D., ``{Hardware/software partitioning in embedded system design. In: Proceedings of the International Symposium of Intelligent Signal Processing},'' pp. 192-202 (2003)

%2
\bibitem{Mann2007}
Mann, Z.A., Orbán, A., Arató, P., ``{Finding optimal hardware/software partitions. In: Formal Methods in System Design, vol. 31},'' {\em Springer}, pp. 241-263.

@@

%22
\bibitem{Arató2005}
Arató, P., Mann, Z.A., Orbán, A. ``{Algorithmic aspects of hardware/software partitioning. In: Association Computing Machinery Transactions on Design Automation of Electronic Systems, vol. 1},'' pp. 136–156 (2005)

@@

%24
\bibitem{DeMoura2008}
De Moura, L., Bjørner, N. ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 4963},'' pp. 337–340, Springer (2008)

@@

%34
\bibitem{Bjørner2014}
Nikolaj Bjorner and Anh-Dung Phan ``{vZ - Maximal Satisfaction with Z3. SCSS 2014. 6th International Symposium on Symbolic Computation in Software Science.}''

>>>>

%----------------------------------------------
\subsection{OpenMP}
%----------------------------------------------

\textcolor{blue}{The OpenMP is a set of directives that augments the C/C++ and Fortran languages. OpenMP uses the fork-join model of parallel execution}

@@

%1
\bibitem{Arato2003}
Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D., ``{Hardware/software partitioning in embedded system design. In: Proceedings of the International Symposium of Intelligent Signal Processing},'' pp. 192-202 (2003)

%2
\bibitem{Mann2007}
Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions. In: Formal Methods in System Design, vol. 31},'' {\em Springer}, pp. 241-263.

@@

%22
\bibitem{Arato2005}
Arat\'o, P., Mann, Z.A., Orb\'an, A. ``{Algorithmic aspects of hardware/software partitioning. In: Association Computing Machinery Transactions on Design Automation of Electronic Systems, vol. 1},'' pp. 136–156 (2005)

@@

%24
\bibitem{DeMoura2008}
De Moura, L., Bjorner, N. ``{Z3: An Efficient SMT Solver. In: Tools and Algorithms for the Construction and Analysis of Systems (TACAS), LNCS 4963},'' pp. 337–340, Springer (2008)

@@

%34
\bibitem{Bjorner2014}
Nikolaj Bjorner and Anh-Dung Phan ``{vZ - Maximal Satisfaction with Z3. SCSS 2014. 6th International Symposium on Symbolic Computation in Software Science.}''
